Towards the Internet of Things: A Real-World Testbed

### 2013-06-11 doc/paper- towards the internet of things/paper v1.tex

\documentclass[conference]{IEEEtran}
\ifCLASSINFOpdf
\else
\fi
\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}

\title{Towards the Internet of Things: A Real-World Testbed}
\author{\IEEEauthorblockN{Nacer Khalil}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: n.khalil@aui.ma}
\and
\IEEEauthorblockN{Mohammed Riduane Abid}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: r.abid@aui.ma}
\and
\IEEEauthorblockN{Driss Benhaddou}
\IEEEauthorblockA{School of Engineering and Technology\\
University of Houston\\
Email: dbenhaddou@uh.edu}}
\maketitle
\begin{abstract}
The internet has seen its importance grow exponentially throughout the previous two decades. It has started as set of computers sharing static information written by human beings and accessed by other human beings. It followed mainly the publisher subscriber model. Later on, with the arrival of internet 2.0, the subscriber had now the ability to affect the content at the publisher's level and this basic idea gave rise to a whole new world of applications such as wikis, blogs, social networks and other applications. The next revolution in the internet is the introduction of machines as players within the internet. This will allow the machines to intercommunicate between them or what is known as machine-to-machine communication. More and more devices will be able to communicate and thus be part of the internet. This will give rise to a whole new dimension of possibilities as the focus of the internet will not only be human interactions but also machine interactions. As an example of autonomous machines communicating through, the components of smart grids will be part of the internet of things. Devices such as AMI, smart homes, wireless sensor networks will all be part of the internet of things. Any device within the smart grid will be uniquely identified through the network and therefore will be able to communicate. In this paper, we present a real-world testbed for integrating wireless sensors into the internet. The solution uses 6lowPAN, and addresses relevant issues at the level of the gateway. we used legacy hardware and proved communication.
\end{abstract}

@@

\section{Internet of things}
The internet of things is a new concept based on the idea that there will be much more users that are computers, machine than human beings. This means that machines will play an important role in the internet and they will be able to communicate autonomously without the interaction of human beings. Wireless sensor network will be part of the internet of things and therefore will be actively communicating in the internet by sending sensor data. Nowadays, the internet is mainly based on a human-to-human. In the future of internet called the internet of things, we will have in addition to human-to-human communication, human-to-machine communication and machine-to-machine communication. An example of human-to-machine communication is when the human will be able to control the wireless sensor network's sampling time. An example of machine-to-machine communication which will be discussed in this paper is the middleware being able to turn off the light because no one is in the room. The middleware by making use of the sensor data will communicate with motes to turn on or off the light bulb.
\section{6lowpan}
6loWPAN stands for  "IPv6 over Low power Wireless Personal Area Networks".

@@

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}

\begin{document}

\title{Towards the Internet of Things: A Real-World Testbed}
\author{\IEEEauthorblockN{Nacer Khalil}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: n.khalil@aui.ma}
\and
\IEEEauthorblockN{Mohamed Riduan Abid}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: r.abid@aui.ma}
\and
\IEEEauthorblockN{Driss Benhaddou}
\IEEEauthorblockA{School of Engineering and Technology\\
University of Houston\\
Email: dbenhaddou@uh.edu}}
\maketitle
\begin{abstract}
The internet has seen its importance grow exponentially throughout the previous two decades. It has started as set of computers sharing static information written by human beings and accessed by other human beings. It followed mainly the publisher subscriber model. Later on, with the arrival of internet 2.0, the subscriber had now the ability to affect the content at the publisher's level and this basic idea gave rise to a whole new world of applications such as wikis, blogs, social networks and other applications. The next revolution in the internet is the introduction of machines as players within the internet. This will allow the machines to intercommunicate between them or what is known as machine-to-machine communication. More and more devices will be able to communicate and thus be part of the internet. This will give rise to a whole new dimension of possibilities as the focus of the internet will not only be human interactions but also machine interactions. As an example of autonomous machines communicating through, the components of smart grids will be part of the internet of things. Devices such as AMI, smart homes, wireless sensor networks will all be part of the internet of things. Any device within the smart grid will be uniquely identified through the network and therefore will be able to communicate. In this paper, we present a real-world testbed for integrating wireless sensors into the internet. The solution uses 6lowPAN, and addresses relevant issues at the level of the gateway. we used legacy hardware and proved communication.
\end{abstract}

@@

\section{Internet of things}
The internet of things is a new concept based on the idea that there will be much more users that are computers, machine than human beings. This means that machines will play an important role in the internet and they will be able to communicate autonomously without the interaction of human beings. Wireless sensor network will be part of the internet of things and therefore will be actively communicating in the internet by sending sensor data. Nowadays, the internet is mainly based on a human-to-human. In the future of internet called the internet of things, we will have in addition to human-to-human communication, human-to-machine communication and machine-to-machine communication. An example of human-to-machine communication is when the human will be able to control the wireless sensor network's sampling time. An example of machine-to-machine communication which will be discussed in this paper is the middleware being able to turn off the light because no one is in the room. The middleware by making use of the sensor data will communicate with motes to turn on or off the light bulb.
\section{6lowpan}
6loWPAN stands for  "IPv6 over Low power Wireless Personal Area Networks". It stands for the name of the working group within IETF. It is based on the idea that all the devices independently of their processing power or energy resources should be able to have the TCP-IP protocol stack and be part of the internet of things. In order to be able to build the T
CP-IP protocol stack in low-power devices, there have been multiple aspects of the protocol stack that has to be optimized. As an example, the IP MTU(maximum transmission unit)

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.5]{images/network_diagram.jpg}
\caption{Network diagram}
\label{fig:network}
\end{figure}
